---
title: "learnr basics"
output:
  learnr::tutorial:
    progressive: true
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(tidyverse)
library(palmerpenguins) #load any packages here that you want to be part of the environment for everyone using the tutorial
library(learnr)

knitr::opts_chunk$set(echo = FALSE)
gradethis::gradethis_setup() # add answer checking for exercises
```

## The basics
`{learnr}` provides a space where people can write and run code, in an environment that runs on a server. This means that everyone has the same version of R, same package versions, etc. It's useful for teaching coding concepts, especially when you're remote and can't troubleshoot with everyone.

`{learnr}` uses `runtime: shiny_prerendered` to turn Markdown files into live tutorials. 

### Exercise 1a
Look at the `penguins` dataset from `{palmerpenguins}`.


```{r ex1a, exercise=TRUE}
penguins 
```
*Note that the `penguins` object is already in the environment!

### Exercise 1b

Plot a scatterplot of bill length (`bill_length_mm`) vs. bill depth (`bill_depth_mm`) from the `palmerpenguins` dataset.

```{r ex1b, exercise=TRUE}
ggplot(penguins, 
       aes (x = bill_length_mm,
            y = bill_depth_mm)) + 
  geom_point()
```


## Hints

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaluated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediately below labeled `print-limit-hint`.*

Filter the penguins dataset to Adelie penguins only.

```{r penguinfilter, exercise=TRUE, exercise.eval=TRUE}
penguins
```

```{r penguinfilter-hint}
penguins %>% filter(species == "Adelie")
```

## Solutions and code-checking

All the previous sections just provide a "safe" coding environment. If you want to quiz people on a topic, you need to provide a solution in the .Rmd file. 

### Exercise with a solution

*Here's a simple exercise with an empty code chunk provided for entering the answer.* 

Write the R code required to add two plus two:

```{r ex2, exercise=TRUE}

```

```{r ex2-solution}
2+2
```

```{r ex2-code-check}
grade_code()
```

To add a "solution" button in the exercise window, add `{r eval = FALSE} gradethis::gradethis_setup()` to the r setup at the beginning of the file, and add another code chunk with the suffix `{r eval = FALSE} -solution`. Using the same example above, add the following chunks to your .Rmd file:

1. The original exercise = TRUE code chunk: r two-plus-two-b  exercise = TRUE
2. Another code chunk called `{r eval = FALSE} r ex2-solution` containing the code you want them to write
3. A third code chunk called `{r eval = FALSE} r ex2-code-check` containing a single line: `{r eval = FALSE} grade_code()`

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```


## Quizzes
### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

